Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-10-18 paper/paper.Rmd
minor improvements in word choice

Partitioning objects in \pkg{mlr3spatiotempcv} are equipped with generic `plot()` and `autoplot()` methods to visualize the created partitions.
`autoplot()` is \pkg{ggplot2}-based and uses [ggplot2](https://ggplot2.tidyverse.org) [@ggplot2] in two-dimensional geographic space and [plotly](https://github.com/ropensci/plotly) [@plotly] in the three dimensions case, i.e., geographic space plus time.

@@

The following example uses $k$-means clustering to generate classes that are used as blocks.
To underline the honoring of the groups, a number of groups (eight) that is not a multiple of the number of folds (three) was chosen.
The test sets in the first and second folds are therefore composed out of three groups while the third one holds two groups.

@@

In this section the `cookfarm` dataset is used as an example because it comes with a temporal dimension via variable "Date".

>>>>

Partitioning objects in \pkg{mlr3spatiotempcv} are equipped with generic `plot()` and `autoplot()` methods to visualize the created partitions.
`autoplot()` is \pkg{ggplot2}-based and uses [ggplot2](https://ggplot2.tidyverse.org) [@ggplot2] in two-dimensional geographic space and [plotly](https://github.com/ropensci/plotly) [@plotly] in the three dimensional case, i.e., geographic space plus time.

@@

The following example uses $k$-means clustering to generate classes that are used as blocks.
To underline the honoring of the groups, a number of groups (eight) that is not a multiple of the number of folds (three) was chosen.
The test sets in the first and second folds are therefore composed of three groups while the third one holds two groups.

@@

In this section the `cookfarm` dataset is used as an example because it has a temporal dimension identified by the variable "Date".
